Advantages of mixed unitary operators for quantum information processing

### 2018-12-28 decorrelation/mixed_unitaries.tex
campbell and hastings reference

Despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs. Drifting control parameters or environmental variables can easily have long correlation times that result in errors which is strongly coherent over the length of a quantum circuit. While these errors can often be reconstructed using various tomographic techniques, their impact is difficult to predict. The diamond distance can be used to estimate the failure probability of a quantum circuit, but the diamond distance can grow quadratically with repeated application of gate with coherent errors. For long circuits, this can add up extremely quickly. Recent work by Hastings and Campbell, however, has shown that coherent noise can be strongly suppressed by probabilistic sampling over various implementations of the target quantum gates. This averaging results in quantum processes with diamond distances that grow only linearly  quadratic in the over/under rotation angle of the component gates. \note{Clear this up.}

>>>>

Despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs. Drifting control parameters or environmental variables can easily have long correlation times that result in errors which is strongly coherent over the length of a quantum circuit. While these errors can often be reconstructed using various tomographic techniques, their impact is difficult to predict. The diamond distance can be used to estimate the failure probability of a quantum circuit, but the diamond distance can grow quadratically with repeated application of gate with coherent errors. For long circuits, this can add up extremely quickly. Recent work by Hastings and Campbell\cite{Campbell2017, 1612.01011, 1811.08017}, however, has shown that coherent noise can be strongly suppressed by probabilistic sampling over various implementations of the target quantum gates. This averaging results in quantum processes with diamond distances that grow only linearly  quadratic in the over/under rotation angle of the component gates. \note{Clear this up.}
